More flexibility reduces social donations

### 2020-08-27 article-elsevier/article-elsevier.Rmd
Actualización de figuras y graficos

---
title: More flexibility reduces social donations
author:
  - name: Sebastián Cea-Echenique
    email: sebastian.cea@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
    footnote: 1
  - name: Claudia Toledo-Aguirre
    email: claudia@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
#   - name: Cat Memes
#     email: cat@example.com
#     affiliation: Another University
#     footnote: 2
#   - name: Derek Zoolander
#     email: derek@example.com
#     affiliation: Some Institute of Technology
#     footnote: 2
# address:
#   - code: Some Institute of Technology
#     address: Department, Street, City, State, Zip
#   - code: Another University
#     address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  # - code: 2
    # text: "Equal contribution"
abstract: |
  We exploit a change in tax donations' law to evaluate a change to more flexibility.

journal: "Economics Letters or Journal of Public Economics"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

@@

@@

The law 19.885 concerning social donations in Chile in his first version on 2003, establishes a tributary benefit of 50\% of the donation as credit discount and the other 50\% consider as spending to make the donation. To receive this benefit the donor must donate a minimum of the 33\% of the donation to the Mixed Fund (MF<!--footnote -->). In this version of the law the limit of the donation was 4.5\% of the taxable liquid income and benefit was equally independent of the amount of the donation.

@@

1. If the donation is less that 1000 UTM (UTM<!--footnote -->) the benefit is 50\% as tributary credit and 50\% as spending. In the case that the donor is a firm, it must donate at as least two different charitable institutions and the donation for each one has to be less than 700 UTM.

@@

@@

@@

<!--preguntar por figuras -->

>>>>

---
title: More flexibility reduces social donations
author:
  - name: Sebastián Cea-Echenique
    email: sebastian.cea@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
    footnote: 1
  - name: Claudia Toledo-Aguirre
    email: claudia.toledo@pucv.cl
    affiliation: School of Industrial Engineering, Pontificia Universidad Católica de Valparaíso
#   - name: Cat Memes
#     email: cat@example.com
#     affiliation: Another University
#     footnote: 2
#   - name: Derek Zoolander
#     email: derek@example.com
#     affiliation: Some Institute of Technology
#     footnote: 2
# address:
#   - code: Some Institute of Technology
#     address: Department, Street, City, State, Zip
#   - code: Another University
#     address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  # - code: 2
    # text: "Equal contribution"
abstract: |
  We exploit a change in tax donations' law to evaluate a change to more flexibility.

journal: "Economics Letters or Journal of Public Economics"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
header-includes:
   - \usepackage{physics}
   - \usepackage{amsmath}
   - \usepackage{tikz}
   - \usepackage{mathdots}
   - \usepackage{yhmath}
   - \usepackage{cancel}
   - \usepackage{color}
   - \usepackage{siunitx}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{amssymb}
   - \usepackage{gensymb}
   - \usepackage{tabularx}
   - \usepackage{booktabs}
   - \usetikzlibrary{fadings}
   - \usetikzlibrary{patterns}
   - \usetikzlibrary{shadows.blur}
   - \usetikzlibrary{shapes}

#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

@@

```{r setup, include=FALSE,echo = FALSE,message=FALSE,warning = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::include_graphics
library(lubridate)
library(stringr)
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(summarytools)
library(panelr)

load("~/workspace/donationstax/Donaciones_total_graficos.Rdata")
load("~/workspace/donationstax/iteraciones/Datos_seleccion_modelo.Rdata")
knitr::opts_chunk$set(fig.width=5, fig.height=5)

@@

The law 19.885 (Fig (\ref{fig:law 19885})) concerning social donations in Chile in his first version on 2003, establishes a tributary benefit of 50\% of the donation as credit discount and the other 50\% consider as spending to make the donation. To receive this benefit the donor must donate a minimum of the 33\% of the donation to the Mixed Fund (MF^[It is a Fund created by the Law on Donations with Social Purposes to support initiatives that civil society organizations present and that directly benefit people in poverty and / or people with disabilities. The Fund's resources come from donations from companies and individuals. Fund resources must be distributed through public tenders. Ministry of social development and family]). In this version of the law the limit of the donation was 4.5\% of the taxable liquid income and benefit was equally independent of the amount of the donation.

\tikzset{every picture/.style={line width=0.75pt}} 
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
\centering
\label{fig:law 19885}
\draw  [draw opacity=0][fill={rgb, 255:red, 194; green, 195; blue, 196 }  ,fill opacity=0.56 ] (81.23,63.8) .. controls (81.23,62.25) and (82.48,61) .. (84.03,61) -- (252.7,61) .. controls (254.25,61) and (255.5,62.25) .. (255.5,63.8) -- (255.5,72.2) .. controls (255.5,73.75) and (254.25,75) .. (252.7,75) -- (84.03,75) .. controls (82.48,75) and (81.23,73.75) .. (81.23,72.2) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 61; green, 151; blue, 237 }  ,fill opacity=0.38 ] (81.5,49.28) .. controls (81.5,47.8) and (82.7,46.6) .. (84.18,46.6) -- (164.82,46.6) .. controls (166.3,46.6) and (167.5,47.8) .. (167.5,49.28) -- (167.5,57.32) .. controls (167.5,58.8) and (166.3,60) .. (164.82,60) -- (84.18,60) .. controls (82.7,60) and (81.5,58.8) .. (81.5,57.32) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 242; green, 152; blue, 65 }  ,fill opacity=0.38 ] (167.5,49.28) .. controls (167.5,47.69) and (168.79,46.4) .. (170.38,46.4) -- (250.25,46.4) .. controls (251.84,46.4) and (253.13,47.69) .. (253.13,49.28) -- (253.13,57.92) .. controls (253.13,59.51) and (251.84,60.8) .. (250.25,60.8) -- (170.38,60.8) .. controls (168.79,60.8) and (167.5,59.51) .. (167.5,57.92) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.38 ] (81.23,78.8) .. controls (81.23,76.84) and (82.82,75.25) .. (84.78,75.25) -- (128.95,75.25) .. controls (130.91,75.25) and (132.5,76.84) .. (132.5,78.8) -- (132.5,89.45) .. controls (132.5,91.41) and (130.91,93) .. (128.95,93) -- (84.78,93) .. controls (82.82,93) and (81.23,91.41) .. (81.23,89.45) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (255.19,37.21) -- (255.31,84.39) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (132.49,63.5) -- (132.51,94.1) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (131.95,93) -- (162.37,93.74) ;
\draw [shift={(166.37,93.83)}, rotate = 181.39] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (81.5,61) -- (252.25,60.8) ;
\draw [shift={(255.25,60.8)}, rotate = 539.9300000000001] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;

\draw (51.67,59.33) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
\draw (125,53.5) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
\draw (210.31,52.6) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
\draw (260.67,27.83) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
\draw (106.87,83.48) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 33\% MF}}};
\end{tikzpicture}

@@

1. If the donation is less that 1000 UTM^[Monthly Tax Unit ("Unidad Tributaria Mensual" in spanish): Unit defined in Chile that corresponds to an amount of money expressed in pesos and determined by law, which is permanently updated by the Consumer Price Index and is used as a tax measure. SII, Basic Tax Accounting Dictionary] the benefit is 50\% as tributary credit and 50\% as spending. In the case that the donor is a firm, it must donate at as least two different charitable institutions and the donation for each one has to be less than 700 UTM.

\tikzset{every picture/.style={line width=0.75pt}}

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (66.61,55.57) .. controls (66.61,54.26) and (67.67,53.2) .. (68.98,53.2) -- (238.74,53.2) .. controls (240.05,53.2) and (241.11,54.26) .. (241.11,55.57) -- (241.11,62.68) .. controls (241.11,63.98) and (240.05,65.04) .. (238.74,65.04) -- (68.98,65.04) .. controls (67.67,65.04) and (66.61,63.98) .. (66.61,62.68) -- cycle ;
\draw   (238.5,66.84) .. controls (190.77,71.51) and (162.13,76.18) .. (152.58,80.84) .. controls (143.04,76.18) and (114.4,71.51) .. (66.67,66.84) ;
\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (152.92,41.68) .. controls (152.92,40.09) and (154.21,38.8) .. (155.8,38.8) -- (237.74,38.8) .. controls (239.33,38.8) and (240.62,40.09) .. (240.62,41.68) -- (240.62,50.32) .. controls (240.62,51.91) and (239.33,53.2) .. (237.74,53.2) -- (155.8,53.2) .. controls (154.21,53.2) and (152.92,51.91) .. (152.92,50.32) -- cycle ;
%Straight Lines [id:da16254432206470004] 
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (242.5,31.84) -- (242.5,75.84) ;
\draw  [draw opacity=0][fill={rgb, 255:red, 61; green, 151; blue, 237 }  ,fill opacity=0.38 ] (66.92,42.28) .. controls (66.92,40.8) and (68.12,39.6) .. (69.6,39.6) -- (150.24,39.6) .. controls (151.72,39.6) and (152.92,40.8) .. (152.92,42.28) -- (152.92,50.32) .. controls (152.92,51.8) and (151.72,53) .. (150.24,53) -- (69.6,53) .. controls (68.12,53) and (66.92,51.8) .. (66.92,50.32) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (67.03,53.3) -- (239.5,51.87) ;
\draw [shift={(242.5,51.84)}, rotate = 539.52] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;

\draw (44,16) node   [align=left] {{\fontfamily{ptm}\selectfont Case 1.}};
\draw (37.33,51) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
\draw (279.33,49) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 1000 U.T.M.}}};
\draw (156.33,101) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Sets of donation to at least 2 differents institutions }}\\{\fontfamily{ptm}\selectfont {\small with each donation below 700 UTM}}};
\draw (109.92,46.3) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
\draw (196.77,44) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
\draw (247.33,21) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
\\*
\end{tikzpicture}

@@

\tikzset{every picture/.style={line width=0.75pt}}
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (61.8,68.97) .. controls (61.8,67.33) and (63.13,66) .. (64.77,66) -- (113.53,66) .. controls (115.17,66) and (116.5,67.33) .. (116.5,68.97) -- (116.5,77.88) .. controls (116.5,79.51) and (115.17,80.84) .. (113.53,80.84) -- (64.77,80.84) .. controls (63.13,80.84) and (61.8,79.51) .. (61.8,77.88) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (62.2,55.73) .. controls (62.2,54.31) and (63.35,53.16) .. (64.77,53.16) -- (231.64,53.16) .. controls (233.06,53.16) and (234.21,54.31) .. (234.21,55.73) -- (234.21,63.43) .. controls (234.21,64.85) and (233.06,66) .. (231.64,66) -- (64.77,66) .. controls (63.35,66) and (62.2,64.85) .. (62.2,63.43) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (147.92,41.28) .. controls (147.92,39.61) and (149.27,38.26) .. (150.94,38.26) -- (230.99,38.26) .. controls (232.66,38.26) and (234.01,39.61) .. (234.01,41.28) -- (234.01,50.33) .. controls (234.01,51.99) and (232.66,53.34) .. (230.99,53.34) -- (150.94,53.34) .. controls (149.27,53.34) and (147.92,51.99) .. (147.92,50.33) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (235.42,33.26) -- (235.5,72.84) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (116.42,53.39) -- (116.58,84.55) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (115.53,83.84) -- (141.14,84.23) ;
\draw [shift={(145.14,84.29)}, rotate = 180.87] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (60.8,139.97) .. controls (60.8,138.33) and (62.13,137) .. (63.77,137) -- (112.53,137) .. controls (114.17,137) and (115.5,138.33) .. (115.5,139.97) -- (115.5,148.88) .. controls (115.5,150.51) and (114.17,151.84) .. (112.53,151.84) -- (63.77,151.84) .. controls (62.13,151.84) and (60.8,150.51) .. (60.8,148.88) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (60.46,127.37) .. controls (60.46,125.97) and (61.59,124.84) .. (62.99,124.84) -- (232.23,124.84) .. controls (233.62,124.84) and (234.75,125.97) .. (234.75,127.37) -- (234.75,134.95) .. controls (234.75,136.34) and (233.62,137.47) .. (232.23,137.47) -- (62.99,137.47) .. controls (61.59,137.47) and (60.46,136.34) .. (60.46,134.95) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (235.42,108.26) -- (235.58,139.43) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (115.42,124.39) -- (115.58,155.55) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (114.73,157.38) -- (85.33,156.9) ;
\draw [shift={(81.33,156.83)}, rotate = 360.94] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
\draw  [draw opacity=0][fill={rgb, 255:red, 61; green, 151; blue, 237 }  ,fill opacity=0.38 ] (61.92,42.28) .. controls (61.92,40.8) and (63.12,39.6) .. (64.6,39.6) -- (145.24,39.6) .. controls (146.72,39.6) and (147.92,40.8) .. (147.92,42.28) -- (147.92,50.32) .. controls (147.92,51.8) and (146.72,53) .. (145.24,53) -- (64.6,53) .. controls (63.12,53) and (61.92,51.8) .. (61.92,50.32) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 61; green, 151; blue, 237 }  ,fill opacity=0.38 ] (61.21,112.62) .. controls (61.21,111.07) and (62.47,109.82) .. (64.02,109.82) -- (127.69,109.82) .. controls (129.24,109.82) and (130.5,111.07) .. (130.5,112.62) -- (130.5,121.04) .. controls (130.5,122.59) and (129.24,123.84) .. (127.69,123.84) -- (64.02,123.84) .. controls (62.47,123.84) and (61.21,122.59) .. (61.21,121.04) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (130.5,112.55) .. controls (130.5,110.85) and (131.88,109.47) .. (133.57,109.47) -- (230.23,109.47) .. controls (231.92,109.47) and (233.3,110.85) .. (233.3,112.55) -- (233.3,121.77) .. controls (233.3,123.47) and (231.92,124.84) .. (230.23,124.84) -- (133.57,124.84) .. controls (131.88,124.84) and (130.5,123.47) .. (130.5,121.77) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (61.03,124.3) -- (232.5,123.85) ;
\draw [shift={(235.5,123.84)}, rotate = 539.85] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (62.03,53.3) -- (233.5,52.85) ;
\draw [shift={(236.5,52.84)}, rotate = 539.85] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
\draw (104.92,47.3) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
\draw (190.96,45.8) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
\draw (240.33,25) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
\draw (89.22,73) node  [font=\small] [align=left] {{\small {\fontfamily{ptm}\selectfont 33\% MF}}};
\draw (279.33,123) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small > 1000 U.T.M.}}};
\draw (96.21,116.52) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 35\% Credit}}};
\draw (179.26,116.01) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 75\% Expense}}};
\draw (239.33,102) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
\draw (87.22,144) node  [font=\small] [align=left] {{\small {\fontfamily{ptm}\selectfont 33\% MF}}};
\draw (277.33,52) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small  > 1000 U.T.M.}}};
\draw (35.33,53) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
\draw (33,125) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
\draw (43,18) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont Case 2.}};
\end{tikzpicture}

@@

\tikzset{every picture/.style={line width=0.75pt}} 
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (79.03,69.3) -- (233.5,68.85) ;
\draw [shift={(236.5,68.84)}, rotate = 539.8299999999999] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (79,71.57) .. controls (79,70.15) and (80.15,69) .. (81.57,69) -- (230.93,69) .. controls (232.35,69) and (233.5,70.15) .. (233.5,71.57) -- (233.5,79.28) .. controls (233.5,80.69) and (232.35,81.84) .. (230.93,81.84) -- (81.57,81.84) .. controls (80.15,81.84) and (79,80.69) .. (79,79.28) -- cycle ;
\draw   (232.5,85) .. controls (189.77,88.95) and (164.13,92.9) .. (155.58,96.84) .. controls (147.04,92.9) and (121.4,88.95) .. (78.67,85) ;
\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (78.88,57.3) .. controls (78.88,55.57) and (80.29,54.17) .. (82.02,54.17) -- (155.36,54.17) .. controls (157.1,54.17) and (158.5,55.57) .. (158.5,57.3) -- (158.5,66.71) .. controls (158.5,68.44) and (157.1,69.84) .. (155.36,69.84) -- (82.02,69.84) .. controls (80.29,69.84) and (78.88,68.44) .. (78.88,66.71) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (157.65,57.3) .. controls (157.65,55.72) and (158.92,54.45) .. (160.5,54.45) -- (230.99,54.45) .. controls (232.57,54.45) and (233.85,55.72) .. (233.85,57.3) -- (233.85,65.86) .. controls (233.85,67.43) and (232.57,68.71) .. (230.99,68.71) -- (160.5,68.71) .. controls (158.92,68.71) and (157.65,67.43) .. (157.65,65.86) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (236.42,53.26) -- (236.58,84.43) ;
\draw (44.33,66) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 1000 U.T.M.}}};
\draw (280.33,68) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 2000 U.T.M..}}};
\draw (118.69,62.01) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
\draw (195.75,60.58) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Expense}}};
\draw (241.33,43) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 100 \%}}};
\draw (52,30) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont Case 3.}};
\draw (169.33,113) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small Sets of donation to at least 2 differents institutions }}\\{\fontfamily{ptm}\selectfont {\small (differents from Case 1.) with each donation below 700 UTM}}};

\end{tikzpicture}

@@

\tikzset{every picture/.style={line width=0.75pt}} 
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (53.8,70.37) .. controls (53.8,68.51) and (55.31,67) .. (57.17,67) -- (95.13,67) .. controls (96.99,67) and (98.5,68.51) .. (98.5,70.37) -- (98.5,80.47) .. controls (98.5,82.34) and (96.99,83.84) .. (95.13,83.84) -- (57.17,83.84) .. controls (55.31,83.84) and (53.8,82.34) .. (53.8,80.47) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (54,57.77) .. controls (54,56.24) and (55.24,55) .. (56.77,55) -- (208.73,55) .. controls (210.26,55) and (211.5,56.24) .. (211.5,57.77) -- (211.5,66.08) .. controls (211.5,67.6) and (210.26,68.84) .. (208.73,68.84) -- (56.77,68.84) .. controls (55.24,68.84) and (54,67.6) .. (54,66.08) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (133.08,41.86) .. controls (133.08,40.21) and (134.42,38.86) .. (136.08,38.86) -- (209.33,38.86) .. controls (210.99,38.86) and (212.33,40.21) .. (212.33,41.86) -- (212.33,50.86) .. controls (212.33,52.52) and (210.99,53.86) .. (209.33,53.86) -- (136.08,53.86) .. controls (134.42,53.86) and (133.08,52.52) .. (133.08,50.86) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (212.42,36.26) -- (212.5,72.84) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (98.42,54.79) -- (98.58,85.95) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (97.13,84.84) -- (122.74,85.23) ;
\draw [shift={(126.74,85.29)}, rotate = 180.87] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
\draw  [draw opacity=0][fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=0.33 ] (60.96,128.37) .. controls (60.96,126.97) and (62.09,125.84) .. (63.48,125.84) -- (207.64,125.84) .. controls (209.03,125.84) and (210.16,126.97) .. (210.16,128.37) -- (210.16,135.95) .. controls (210.16,137.34) and (209.03,138.47) .. (207.64,138.47) -- (63.48,138.47) .. controls (62.09,138.47) and (60.96,137.34) .. (60.96,135.95) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (59.88,111.44) .. controls (59.88,109.46) and (61.5,107.84) .. (63.48,107.84) -- (118.9,107.84) .. controls (120.89,107.84) and (122.5,109.46) .. (122.5,111.44) -- (122.5,122.24) .. controls (122.5,124.23) and (120.89,125.84) .. (118.9,125.84) -- (63.48,125.84) .. controls (61.5,125.84) and (59.88,124.23) .. (59.88,122.24) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 245; green, 166; blue, 35 }  ,fill opacity=0.33 ] (122.5,112.04) .. controls (122.5,110.28) and (123.93,108.84) .. (125.7,108.84) -- (206.3,108.84) .. controls (208.07,108.84) and (209.5,110.28) .. (209.5,112.04) -- (209.5,121.64) .. controls (209.5,123.41) and (208.07,124.84) .. (206.3,124.84) -- (125.7,124.84) .. controls (123.93,124.84) and (122.5,123.41) .. (122.5,121.64) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (208.42,107.26) -- (208.5,143.84) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (105.56,127.22) -- (105.73,158.38) ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][line width=1.5]  [dash pattern={on 1.69pt off 2.76pt}]  (105.73,158.38) -- (76.33,157.9) ;
\draw [shift={(72.33,157.83)}, rotate = 360.94] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (13.4,-6.43) -- (0,0) -- (13.4,6.44) -- (8.9,0) -- cycle    ;
\draw  [draw opacity=0][fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=0.33 ] (53.46,41.46) .. controls (53.46,39.73) and (54.87,38.32) .. (56.6,38.32) -- (129.95,38.32) .. controls (131.68,38.32) and (133.08,39.73) .. (133.08,41.46) -- (133.08,50.86) .. controls (133.08,52.6) and (131.68,54) .. (129.95,54) -- (56.6,54) .. controls (54.87,54) and (53.46,52.6) .. (53.46,50.86) -- cycle ;
\draw  [draw opacity=0][fill={rgb, 255:red, 184; green, 233; blue, 134 }  ,fill opacity=0.33 ] (60.52,141.59) .. controls (60.52,139.72) and (62.03,138.22) .. (63.89,138.22) -- (101.86,138.22) .. controls (103.72,138.22) and (105.22,139.72) .. (105.22,141.59) -- (105.22,151.69) .. controls (105.22,153.55) and (103.72,155.06) .. (101.86,155.06) -- (63.89,155.06) .. controls (62.03,155.06) and (60.52,153.55) .. (60.52,151.69) -- cycle ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (61.03,125.3) -- (205.5,124.85) ;
\draw [shift={(208.5,124.84)}, rotate = 539.8199999999999] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
\draw [color={rgb, 255:red, 74; green, 144; blue, 226 }  ,draw opacity=1 ][fill={rgb, 255:red, 241; green, 20; blue, 20 }  ,fill opacity=1 ]   (54.03,54.3) -- (209.5,53.85) ;
\draw [shift={(212.5,53.84)}, rotate = 539.8399999999999] [fill={rgb, 255:red, 74; green, 144; blue, 226 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
\draw (29.33,52) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 0 U.T.M.}}};
\draw (92.07,45.41) node  [font=\small] [align=left] {{\fontfamily{ptm}\selectfont {\small 50\% Credit}}};
